\documentclass[a4paper, 12pt]{article}
\pagenumbering{gobble}
\usepackage[a4paper, top=1cm, bottom=1cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontawesome}

\hypersetup{
	colorlinks=true,
	allcolors=blue!50!black,
}

\setlist[itemize]{leftmargin=*,itemsep=0.5\parskip,topsep=2pt}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0cm}

\newcommand{\resumeSection}[1]{\vspace{12pt}{\Large \bfseries #1} \vspace{-9pt} \\ \rule{\textwidth}{0.7pt}}
\newcommand{\resumeSubsection}[1]{\textbf{#1}}
\newcommand{\resumeFAIcon}[1]{\makebox[24pt][c]{\faicon{#1}}}

\begin{document}
	\begin{center}
		{\huge \bfseries Ata Kuyumcu}

		\begin{tabular}{c c}
			\href{mailto:ata.kuyumcu@yandex.ru}{ata.kuyumcu@yandex.ru} &
			\href{https://ata.gitlab.io}{ata.gitlab.io}
			
		\end{tabular}
	\end{center}

	\vspace{-20pt}
	\resumeSection{\resumeFAIcon{briefcase}Experience}
	
	\resumeSubsection{Full Stack Developer} \hfill Jan 2019  – Present \\
	Countly \hfill Remote
	
	\begin{itemize}
		\item Implemented multiple new features for Countly Community \& Enterprise Editions such as two-factor authentication and JIRA integration.
		\item Maintained and later rewrote the open source C++ SDK used to integrate Countly into native desktop applications.
	\end{itemize}

	\resumeSubsection{Software Developer} \hfill May – Aug 2018 \\
	Özgür Yazılım A.Ş. \hfill Remote
		
	\begin{itemize}
		\item Internationalized a large Ruby on Rails codebase (1 million lines of code) in 3 months.
		\item Worked fully remotely with a distributed team; using GitHub, Pivotal Tracker and Travis CI to collaborate with the QA team and management.
	\end{itemize}

	\resumeSubsection{System Administrator} \hfill Sep 2017 – Feb 2018 \\
	Global Review of Social Sciences \hfill İzmir, Turkey
	
	\begin{itemize}
		\item Recovered the old journal’s database from the backups of a compromised server, preserving the journal layout and the archived articles to set up a new Open Journal Systems instance.
		\item Found the remote code execution vulnerability that led to the breach on the old instance and secured the new one against it.
		\item Maintained server security and availability until the project was canceled.
	\end{itemize}
	
	\resumeSection{\resumeFAIcon{heart}Projects}
	
	\begin{itemize}
		\item \resumeSubsection{\href{https://gitlab.com/Ata/badger}{Badger}:} A web service that generates sleek project badges with data from various APIs such as Travis CI and Liberapay. Built using Kemal, a simple web application library for Crystal.
		\item \resumeSubsection{\href{https://github.com/LVMBDV/blockchan}{Blockchan}:} A proof of concept implementation of a decentralized anonymous imageboard that uses a public, proof-of-work governed blockchain to store and synchronize posts between many peers. Presented as my graduation project in May of 2018.
		\item \resumeSubsection{\href{https://gitlab.com/Ata/thx-1138}{thx-1138}:} A minimalistic hugo theme originally made for \href{https://ata.gitlab.io}{ata.gitlab.io}.
	\end{itemize}
	
	\resumeSection{\resumeFAIcon{graduation-cap}Education}
	
	\begin{itemize}
		\item \resumeSubsection{İzmir University of Economics} \hfill Sep 2014 – Feb 2019 \\
		Bachelor’s Degree in Computer Engineering \hfill İzmir, Turkey
	\end{itemize}

	\newpage
	
	\resumeSection{\resumeFAIcon{users}Organizations}
	
	\begin{itemize}
		\item Community Member at \href{https://dailyprog.gitlab.io}{dailyprog} \hfill Oct 2018 – Present
		\item Team Member at \href{https://twitter.com/Suloband}{SULOBAND} (formerly YubitSec) \hfill Jan 2018 – Present
	\end{itemize}

	\resumeSection{\resumeFAIcon{trophy}Accomplishments}

	\begin{itemize}
		\item 3rd Place Team at \href{https://ctf.stm.com.tr}{STM CTF 2018} Online Qualifiers \hfill Oct 2018
		\item 1st Place Team at \href{http://codeofduty.iyte.edu.tr}{İzHack - Code of Duty 2018} \hfill Mar 2018
	\end{itemize}

	\resumeSection{\resumeFAIcon{envelope}References}
	
	References available upon request.

\end{document}